---
title: "RSTR_Tscm_FlowAnalysis_all_batches"
author: "Nathan Kieswetter - Seshadri Lab"
date: "2024-05-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load appropriate libraries

```{r}
library(here)
library(tidyverse)
library(devtools)
library(scales)
library(tidyselect)
library(readxl)
library(ggpubr)
library(rstatix)
```

# Read in Counts Document

``` {echo="FALSE"}
batch1_2_counts <- read_excel("data/Tscm_flow_batch1_2_counts.xlsx")
```

# Data processing for downstream analysis

## Add RS102 to the beginning of each PTID to identify and segregate PTIDS into groups

```{r }
batch1_2_counts <- batch1_2_counts %>%
  mutate(ptid = paste0("RS102", ptid))
```

## Define P_neg and TST_pos PTIDS and rename to RSTR and LTBI, respectively.

```{r}

p_neg_ptids <- c( "RS102451","RS102510","RS102287","RS102058",
                  "RS102183","RS102346","RS102545","RS102373",
                  "RS102134","RS102438","RS102353","RS102360"
)

tst_pos_ptids <- c("RS102187", "RS102095", "RS102297", "RS102332", "RS102235",
                   "RS102248", "RS102236", "RS102254", "RS102244", "RS102539",
                   "RS102327", "RS102385", "RS102530", "RS102164", "RS102525",
                   "RS102358", "RS102111", "RS102380", "RS102217", "RS102284",
                   "RS102361", "RS102088", "RS102056", "RS102180", "RS102323",
                   "RS102301")

batch1_2_counts <- batch1_2_counts %>%
  mutate(group = case_when(ptid %in% p_neg_ptids ~ "RSTR",
                           ptid %in% tst_pos_ptids ~ "LTBI")
  )
```

### Re-define column names

```{r}

batch1_2_counts <- batch1_2_counts %>%
  rename(  "CD3_CD95_CFSE_low" = "Single Cells/Single Cells/Lymphocytes/Live_CD3/All_CD3_CD95_pos/CFSE_low | Freq. of Live_CD3",
           "CD3_CD95_CFSE_low_CM" = "Single Cells/Single Cells/Lymphocytes/Live_CD3/All_CD3_CD95_pos/CFSE_low/Q1: CD45RA- , CCR7+ | Freq. of Live_CD3",
           "CD3_CD95_CFSE_low_Naive" = "Single Cells/Single Cells/Lymphocytes/Live_CD3/All_CD3_CD95_pos/CFSE_low/Q2: CD45RA+ , CCR7+ | Freq. of Live_CD3",
           "CD3_CD95_CFSE_low_TEMRA" = "Single Cells/Single Cells/Lymphocytes/Live_CD3/All_CD3_CD95_pos/CFSE_low/Q3: CD45RA+ , CCR7- | Freq. of Live_CD3",
           "CD3_CD95_CFSE_low_EM" = "Single Cells/Single Cells/Lymphocytes/Live_CD3/All_CD3_CD95_pos/CFSE_low/Q4: CD45RA- , CCR7- | Freq. of Live_CD3",
           "CD4_CD95_CFSE_low" = "Single Cells/Single Cells/Lymphocytes/Live_CD3/CD4/CD95_pos/CFSE_low | Freq. of Live_CD3",
           "CD4_CD95_CFSE_low_CM" = "Single Cells/Single Cells/Lymphocytes/Live_CD3/CD4/CD95_pos/CFSE_low/Q1: CD45RA- , CCR7+_CM | Freq. of CFSE_low",
           "CD4_CD95_CFSE_low_Naive" = "Single Cells/Single Cells/Lymphocytes/Live_CD3/CD4/CD95_pos/CFSE_low/Q2: CD45RA+ , CCR7+_Naive | Freq. of CFSE_low",
           "CD4_CD95_CFSE_low_TEMRA" = "Single Cells/Single Cells/Lymphocytes/Live_CD3/CD4/CD95_pos/CFSE_low/Q3: CD45RA+ , CCR7-_TEMRA | Freq. of CFSE_low",
           "CD4_CD95_CFSE_low_EM" = "Single Cells/Single Cells/Lymphocytes/Live_CD3/CD4/CD95_pos/CFSE_low/Q4: CD45RA- , CCR7-_EF | Freq. of CFSE_low"
           )
```

## Remove any PTIDS that have no CD95+ cells

```{r}
batch1_2_counts <- batch1_2_counts %>%
  filter(CD3_CD95_CFSE_low != 0) %>%
  filter(stim != "DMSO")

batch1_2_counts <- batch1_2_counts %>%
  mutate(group = factor(group, levels = c("RSTR", "LTBI")))

batch1_2_counts_pp1 <- batch1_2_counts %>%
  filter(stim == "PP1")
```

## Plot All CD95+ cells of CD3+CD4+CD8- cells

```{r}
ggplot(batch1_2_counts,
       aes(x = stim,
           y = CD4_CD95_CFSE_low,
           color = group)) +
  labs(fill = 'Group') +
  geom_boxplot(outlier.shape = NA) +
  geom_point(position = position_jitterdodge(jitter.width = 0.1)) +
  theme(plot.title = element_text(hjust = 0.5))+
  theme_bw() +
  theme(text = element_text(family="Arial", size=22),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        plot.title = element_text(hjust = 0.5),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
   scale_color_manual(values = c("#984EA3","#4DAF4A"))
  stat_compare_means(method = "wilcox.test")
```

# Code to assess memory phenotypes within each stimulation condition

## Filter the memory populations

```{r}
memory_subset <- batch1_2_counts %>%
  pivot_longer(cols = 4:13,
              names_to = "memory",
              values_to = "frequency") %>%
  filter(memory %in% c("CD4_CD95_CFSE_low_CM", 
                       "CD4_CD95_CFSE_low_Naive", 
                       "CD4_CD95_CFSE_low_TEMRA", 
                       "CD4_CD95_CFSE_low_EM")) %>%
  mutate(memory = str_remove(memory, "CD4_CD95_CFSE_low_")) %>%
  filter(stim != "DMSO")
```

## Subset the stimulated populations so that they can be plotted individually

```{r}
memory_subset_MTBL <- memory_subset %>%
  filter(stim == "MTBL" & 
        memory != "Naive" & 
        memory != "TEMRA")
memory_subset_PP1 <- memory_subset %>%
  filter(stim == "PP1" & 
        memory != "Naive" & 
        memory != "TEMRA")
```

### Mtb Stimulated Samples Plot

```{r}
ggplot(memory_subset_MTBL,
       aes(x = memory,
           y = frequency)) +
  geom_boxplot(outlier.shape = NA) + 
  geom_jitter(position = position_jitter(width = 0.01, height = 0.2), 
              aes(colour = group), 
              alpha = 0.9) +
  xlab("Memory Population") +
  ylab("Frequency (%)") +
  ggtitle("MTBL",
          subtitle = "Of proliferating CD3+CD4+CD95+ Cells") +
  theme(plot.title = element_text(hjust = 0.5))+
  theme_bw() +
  theme(text = element_text(family="Arial", size=22),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        plot.title = element_text(hjust = 0.5),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  scale_color_manual(values = c("#984EA3","#4DAF4A")) 
  stat_pvalue_manual(stat.test_MTBL,
                     label = "p.adj",
                     y.position = c(118, 110, 105, 75, 65, 55)) +
  stat_compare_means(method = "wilcox.test",
                     label.x = 1.25)
```

### PP1 (ESAT-6/CFP-10) Stimulated Samples Plot

```{r}
 ggplot(memory_subset_PP1,
       aes(x = memory,
           y = frequency)) +
  geom_boxplot(outlier.shape = NA) + 
  geom_jitter(position=position_jitter(width = 0.01, height = 0.2), 
              aes(colour = group), 
              alpha=0.9) +
  xlab("Memory Phenotype") +
  ylab("Frequency (%)") +
  ggtitle("PP1",
          subtitle = "Of proliferating CD3+CD4+CD95+ Cells") +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))+
  theme_bw() +
  theme(text = element_text(family="Arial", size=22),
        axis.text.x = element_text(color="black"),
        axis.text.y = element_text(color="black"),
        plot.title = element_text(hjust = 0.5),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  scale_color_manual(values = c("#984EA3","#4DAF4A"))+
  stat_pvalue_manual(stat.test_PP1,
                     label = "p.adj",
                     y.position = c(118, 110, 105, 100, 95, 35)) +
  stat_compare_means(method = "wilcox.test",
                     label.x = 1.25)
```
